Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-02-06 paper.qmd
Added linked plot for discussion

To understand how well the model fits the points—whether it fits consistently, works better in certain areas, or fails to match the overall pattern—it is important to link and brush the points with high model error in the \pD{} error plot, \gD{} layout, and the generated model overlay on the data in \pD{}.

@@

Diagnose the fitted model is important. Interactivity helps to

>>>>

To understand how well the model fits the points—whether it fits well, works better in some positions, or fails to match the overall pattern—it is important to link and brush the points with high model error in the \pD{} error plot, \gD{} layout, and the generated model overlay on the data in \pD{}.

@@

Diagnose is important to find where the \gD{} points located in \pD{}. One approach is to use interactivity. By linking the \gD{} layout with the fitted model in \pD{} and employing brushing techniques, we can identify which points fit well and which do not. Additionally, linking the \gD{} error plot with the fitted model in \pD{} can help pinpoint where mismatches occur.
